|

### 2023-03-03 inst/MyArticle/prolfqua_supplement.Rmd
fix spelling in author name.

---
title: | 
    | Supporting Information
    | prolfqua : A Comprehensive R-package for Proteomics Differential Expression Analysis
author:
  - Witold E. Wolski:
      email: wew@fgcz.ethz.ethz.ch
      institute: [fgcz, sib]
      correspondence: true
  - Paolo Nanni:
      institute: [fgcz]
  - Jonas Grossmann:
      institute: [fgcz, sib]
  - Maria dErrico:
      institute: [fgcz, sib]
  - Ralph Schlapbach:
      institute: [fgcz]
  - Christian Panse:
      institute: [fgcz, sib]
institute:
  - fgcz: Functional Genomics Center Zurich (FGCZ), ETH Zurich / University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland
  - sib: Swiss Institute of Bioinformatics (SIB), Quartier Sorge - Batiment Amphipole, 1015 Lausanne, Switzerland
package: prolfqua
output:
  bookdown::pdf_document2:
    toc: yes
    number_sections: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
abstract: |
  This document contains the supplements for the prolfqua manuscript available
  through \url{https://doi.org/10.1101/2022.06.07.494524}.
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
  bibliography: prolfqua.bib 
---

>>>>

---
title: | 
    | Supporting Information
    | prolfqua: A Comprehensive R-package for Proteomics Differential Expression Analysis
author:
  - Witold E. Wolski:
      email: wew@fgcz.ethz.ethz.ch
      institute: [fgcz, sib]
      correspondence: true
  - Paolo Nanni:
      institute: [fgcz]
  - Jonas Grossmann:
      institute: [fgcz, sib]
  - Maria d'Errico:
      institute: [fgcz, sib]
  - Ralph Schlapbach:
      institute: [fgcz]
  - Christian Panse:
      institute: [fgcz, sib]
institute:
  - fgcz: Functional Genomics Center Zurich (FGCZ), ETH Zurich / University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland
  - sib: Swiss Institute of Bioinformatics (SIB), Quartier Sorge - Batiment Amphipole, 1015 Lausanne, Switzerland
package: prolfqua
output:
  bookdown::pdf_document2:
    toc: yes
    number_sections: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
abstract: |
  This document contains the supplements for the prolfqua manuscript available
  through \url{https://doi.org/10.1101/2022.06.07.494524}.
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
  bibliography: prolfqua.bib 
---
